\textsf{Are large language models superhuman chemists?}

### 2024-10-28 src/tex/appendix.tex
fix: correct the failed examples table

%\begin{table}
%    \centering
%    \small
%    \caption{\textbf{Examples of topics evaluated in the \chembench corpus that the state-of-the-art model failed to answer correctly.} The table displays the percentage of questions in the corpus for each topic, along with example questions and the percentage of questions that were not answered correctly by the models.}
%    \label{tab:chembench_corpus_models_failed_topic}
%    {\fontsize{8}{9}\selectfont
%        \begin{tabularx}{\textwidth}{X}
%            \toprule
%            \multicolumn{1}{c}{\textbf{Analytical Questions} 166 Questions (5.8\%) (26.5\%)} \\
%            \midrule
%            Which of the following methods can be used to support the structure elucidation of planar molecules by examining the topography of individual molecules? \\
%            A. DESI-mass spectrometry \\
%            B. XPS \\
%            C. atomic force microscopy \\
%            D. scanning tunneling microscopy \\
%            E. secondary ion mass spectrometry \\
%            \midrule
%            \multicolumn{1}{c}{\textbf{Chemical Preference} 1001 Questions (35\%) (8.5\%)} \\
%            \midrule
%            Imagine an early virtual screening campaign setting (accounting for simple aspects such as oral availability and small molecular profile, but no other modalities such as covalency or bifunctionality). Which of the following two candidates would you prefer for further development? \\
%            [START\_SMILES]N\#Cc1ccc(OCCCN2CC3CN\-(CCNS(=O)(=O)c4ccc(F)cc4)CC(C2)O3)cc1\-[END\-\_SMILES] \\
%            [START\_SMILES]O=C1CC(c2ccc(CC(NS(=O)\-(=O)\-c3cc(Cl)cc(Cl)c3)c3nc4ccccc4[nH]3)cc2)S\-(=O)\-(=O)N1[END\_SMILES] \\
%            \midrule
%            \multicolumn{1}{c}{\textbf{General Chemistry} 152 Questions (5.3\%) (3.2\%)} \\
%            \midrule
%            Why \ce{SCl6} does not exist if other similar molecules such as \ce{SF6} exist? \\
%            A. \ce{SCl6} does not exist because of steric effects \\
%            B. \ce{SCl6} does not exist because of the high electronegativity of chlorine \\
%            C. \ce{SCl6} does not exist because of the high ionization potential of the chlorine \\
%            D. \ce{SF6} exist because of the high electronegativity of fluorine \\
%            \midrule
%            \multicolumn{1}{c}{\textbf{Inorganic Chemistry} 94 Questions (3.3\%) (4.2\%)} \\
%            \midrule
%            What is the spin-only magnetic moment (in units of Bohr-magnetons) for the low-spin case of the metal complex \ce{RhCl(CO)(PPh3)2}?\\
%            \midrule
%            \multicolumn{1}{c}{\textbf{Materials Science} 89 Questions (3.1\%) (0.9\%)} \\
%            \midrule
%            What are the conditions for the observation of effects of quantum confinement in quantum dots? \\
%            A. All dimension of the material must be smaller than exciton Bohr radius \\
%            B. One dimension of the quantum dot must be smaller than exciton Bohr radius \\
%            C. The movement od charge carriers is limited in all spatial dimensions \\
%            \midrule
%            \multicolumn{1}{c}{\textbf{Organic Chemistry} 441 Questions (15.5\%) (0.5\%)} \\
%            \midrule
%            What makes acrylates more reactive than typical hydrocarbons? \\
%            A. The carbonyl group \\
%            B. The double bond \\
%            C. The hydroxyl group \\
%            D. The vinyl group \\
%            \midrule
%            \multicolumn{1}{c}{\textbf{Physical Chemistry} 179 Questions (6.3\%) (13.4\%)} \\
%            \midrule
%            Why are polar molecules more soluble in water than non-polar molecules? \\
%            A. Non-polar molecules should break hydrogen bonds in water to dissolve \\
%            B. The entropy of the system increases when non-polar molecules dissolve in water \\
%            C. Water has a dipole and can easier isolate polar molecules from each other \\
%            D. Water makes stable dipole-dipole interactions with polar molecules \\
%            \midrule
%            \multicolumn{1}{c}{\textbf{Technical Chemistry} 42 Questions (1.5\%) (4.7\%)} \\
%            \midrule
%            Which of the following statements is/are true about granulation shaping of solid catalysts? \\
%            A. Broader product diameter distribution than pellets or extrudates \\
%            B. Facilitates reactor upscaling \\
%            C. It is also called snow-ball \\
%            D. Not suitable to prepare egg-shell catalysts \\
%            \midrule
%            \multicolumn{1}{c}{\textbf{Toxicity/Safety} 690 Questions (24.2\%) (40.4\%)} \\
%            \midrule
%            What determines the flammability of polyols? \\
%            A. Their chemical structure \\
%            B. Their low volatility \\
%            C. Their odor threshold \\
%            D. Their reaction with acids \\
%            \bottomrule
%        \end{tabularx}
%    }
%\end{table}

% \normalsize

% To better understand the cognitive demands of chemical assessment, we categorized the questions in the ChemBench corpus according to the primary skills required to solve them. The table \Cref{tab:chembench_corpus_models_failed_cognitive} below shows representative examples of questions that state-of-the-art models failed to answer correctly across different cognitive skill categories, including knowledge, reasoning and intuition.
% \begin{table}
%     \centering
%     \small
%     \caption{\textbf{Examples of required skills evaluated in the \chembench corpus that the state-of-the-art model failed to answer correctly} The table displays the number of questions for each skill, along with an example question that the model failed to answer.}
%     \label{tab:chembench_corpus_models_failed_cognitive}
%     {\fontsize{8}{9}\selectfont
%         \begin{tabularx}{\textwidth}{X}
%             \toprule
%             \multicolumn{1}{c}{\textbf{Knowledge} 919 Questions} \\
%             \midrule
%             Which of the following are true for phosphoric acid? \\
%             A. Is a weak acid, so it is not toxic \\
%             B. Should never be tasted \\
%             C. Though a component of soft drinks, reacts vigorously with water when in concentrated form \\
%             \midrule
%             \multicolumn{1}{c}{\textbf{Reasoning} 987 Questions} \\
%             \midrule
%             Which of the following elements has the largest atomic radius? \\
%             A. \ce{Fr} \\
%             B. \ce{He} \\
%             C. \ce{Li} \\
%             D. \ce{Rb} \\
%             \midrule
%             \multicolumn{1}{c}{\textbf{Intuition} 1001 Questions} \\
%             \midrule
%             Imagine an early virtual screening campaign setting (accounting for simple aspects such as oral availability and small molecular profile, but no other modalities such as covalency or bifunctionality). Which of the following two candidates would you prefer for further development? \\
%             A. [START\_SMILES]CCc1c(CCOC)nn(-c2ccccc2)c1-c1ccccc1[END\_SMILES] \\
%             B. [START\_SMILES]Cc1cc(/C=C2\\C(=N)N3N=C(S(C)(=O)=O)SC3=NC2=O)c(C)n1Cc1ccccc1[END\_SMILES] \\
%             \midrule
%             \multicolumn{1}{c}{\textbf{Calculation} 128 Questions} \\
%             \midrule
%             The cell potential for the overall cell reaction during electrolysis of water, \ce{2H2O(l) -> 2H2(g) + O2(g)} is \SI{-1.23}{V}. What is the standard electrode potential for the half reaction, \ce{2H2O(l) -> O2(g) + 4H+(aq) + 4e-} in V? \\
%             \bottomrule
%         \end{tabularx}
%     }
% \end{table}

>>>>

\begin{table}
    \centering
    \small
    \caption{\textbf{Examples of some questions failed for all the state-of-the-art models.} The table shows examples of the \chembench corpus for which all models considered in \Cref{fig:human_vs_models_bar} fail to answer correctly.}
    \label{tab:chembench_corpus_cognitive}
    {\fontsize{8}{9}\selectfont
        \begin{tabularx}{\textwidth}{X}
            \toprule
            Which of the following compounds are capable of producing hazardous explosive peroxides? \\
            A. Cyclohexene \\
            B. Cyclooctene \\
            C. Decalin \\
            D. Ethyl ether \\
            E. Isopropyl ether \\
            F. Para-dioxane \\
            G. Tetralin \\
            \midrule
            What is the oxidation number of hydrogen in the reactants of Sabatier reaction? \\
            \midrule
            How does a non-competitive inhibitor influence the enzyme kinetics of a reaction in the Lineweaver-Burk-plot when compared to a competitive inhibitor? \\
            A. The intersection with y-axis shift to higher numbers \\
            B. The intersection with y-axis shift to lower numbers \\
            C. The slope decreases \\
            D. The slope increases \\
            \midrule
            Poly(lactic acid) (PLA) can be broken down enzymatically to lactic acid monomer and compound B (a dimer of lactic acid). A plastic sample degraded to 1.044 g, and titration showed it needed \SI{19.40}{cm^{3}} of \SI{0.100}{mol dm^{-3}} \ce{NaOH} to neutralize. What is the number of moles of acid in the sample? \\
            \midrule
            What is hydrofluoric acid used for? \\
            A. For cleaning facades \\
            B. For etching glass \\
            C. For filling accumulators \\
            D. For soldering \\
            \midrule
            How many chiral centers are present in the molecular structure of citric acid? \\
            \midrule
            What is the sum of the stoichiometric coefficients on the left side of the redox reaction equation: \ce{Cd(NCS)2 + KNO3 -> K2CO3 + CO + SO2 + N2 + CdO}? \\
            A. 10 \\
            B. 14 \\
            C. 18 \\
            D. 23 \\
            E. 9 \\
            \midrule
            The ligand-field splitting energy (LFSE) is computed as $LFSE=-0.4\cdot Dq \cdot n+0.6 \cdot Dq \cdot m$ with $n$ being the number of electrons in t2g d orbitals ($\mathrm{d}_{xz}$, $\mathrm{d}_{yz}$ and $\mathrm{d}_{xy}$), $m$ the number of electrons in eg d orbitals ($\mathrm{d}_{x^2-y^2}$ and $\mathrm{d_{z^2}}$), and Dq the ligand field splitting parameter. What is the value of LFSE in terms of Dq for the low-spin case in the metal complex tetramethylamine diaquacopper(II) ion? \\
            \midrule
            In phenol's mass spectrum, how does the intensity of the m/z 95 peak compare to the molecular ion peak at m/z 94? \\
            A. 10.0\% \\ 
            B. 6.6\% \\
            C. 7.0\% \\
            D. 94\% \\
            \bottomrule
        \end{tabularx}
    }
\end{table}
